Stabilization-Free Virtual Element Methods

### 2023-08-15 stabfreevem_sinum.tex
add mesh asumption
all the faces of each polytope are simplices

% REQUIRED
\begin{abstract}
Virtual element methods (VEMs) without extrinsic stabilization in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions. The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm. Optimal error estimates are derived for these VEMs. Numerical experiments are provided to test the VEMs without extrinsic stabilization.
\end{abstract}

@@

% The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
% the analysis is rather elaborate. 
% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
The key to construct VEMs without extrinsic stabilization is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
inner product $(\cdot, \cdot)_K$. The norm equivalence
\eqref{intro:gradVknormequiv} implies that the space $\mathbb{V}(K)$ should be
sufficiently large compared with the virtual element space $V_k(K)$.  In
standard virtual element methods, $Q_{k-1}^{K}\nabla v$
\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
space $\mathbb P_{k}(K)$.  While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then an additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.
% $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
% Instead, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.

We first construct $H(\div)$-conforming macro finite elements based on a
simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The
shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$-th
order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition
$\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element
space for $k=0$, with some constraints. To ensure the $L^2$ projection
$Q_{K,k}^{\div}\nabla v$ onto the space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
for virtual element function $v\in V_k(K)$, we require that
$\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
$\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$
is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
these considerations and the direct decomposition of an $H(\div)$-conforming
macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
the unisolvent DoFs for the space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
$L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
a conforming finite element for the differential $(d-2)$-form in
\cite{ArnoldFalkWinther2006,Arnold2018}.

@@

By the aid of the projector $Q_{K,k}^{\div}$, we advance a nonconforming VEM without extrinsic stabilization in arbitrary dimension and a conforming VEM without extrinsic stabilization in two dimensions  for second order elliptic problems.
Indeed, these VEMs can be equivalently recast as
primal mixed VEMs.
We prove the norm equivalence~\eqref{intro:gradVknormequiv} and the well-posedness of the VEMs without extrinsic stabilization, and derive the optimal error estimates.

@@

The rest of this paper is organized as follows. Notation and mesh conditions are presented in Section~\ref{sec:prelim}. 
In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed. A nonconforming VEM without extrinsic stabilization in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a conforming VEM without extrinsic stabilization in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
Some numerical results are shown in Section \ref{sec:numericalexamps}.

@@

Given a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively. For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ the unit outward normal vector to $\partial K$, which will be abbreviated as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.

@@

\subsection{Mesh conditions}\label{sec:meshcondition}
We impose the following conditions on the mesh $\mathcal T_h$ in this paper:
\begin{itemize}
 \item[(A1)] Each element $K\in \mathcal T_h$ and each face $F\in \mathcal F_h^r$ for $1\leq r\leq d-1$ is star-shaped with a uniformly bounded chunkiness parameter.

 \item[(A2)] There exists a shape-regular simplicial mesh $\mathcal T_h^*$ such that each $K\in \mathcal T_h$ is a union of some simplexes in $\mathcal T_h^*$. For polytope $K\in \mathcal T_h$, let $\mathcal T_K$ be the simplicial partition of $K$ induced from $\mathcal T_h^*$. Assume simplicial partition $\mathcal T_K$ is quasi-uniform.
\end{itemize}

@@

% For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. 
Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. Set 
\[
\mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
\]

@@

Note that $\div\skw=\curl$ for $d=2,3$.
For $k\geq1$, by finite element complexes \eqref{eq:localBDMfemderhamcomplex}-\eqref{eq:localRTfemderhamcomplex0}, we have
\begin{equation}\label{eq:20220324-4}
\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)-\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\mathcal F^{\partial}(\mathcal T_K)-1.
\end{equation}
% \begin{align*}  
% \dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\mathcal F(\mathcal T_K)+ \left(d{k+d-2\choose d}-{k+d-1\choose d}\right)\#\mathcal T_K, \\
% \dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\mathcal F^i(\mathcal T_K)+ \left(d{k+d-2\choose d}-{k+d-1\choose d}\right)\#\mathcal T_K+1,
% \end{align*}

\subsection{$H(\div)$-conforming macro finite element}
For each polygon $K\in \mathcal T_h$, 
define the shape function space
\[
\boldsymbol{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\},
\]
for $k\geq 2$, and 
\[
\boldsymbol{V}_{0}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{\mathrm{RT}}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\}.
\]
Apparently $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\boldsymbol{V}_{k-1}^{\rm div}(K)$, $\boldsymbol{V}_{0}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_0^{\mathrm{RT}}(K)\cap\ker(\div)$, and $\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$ for $k\geq2$.

In the following lemma we present a direct sum decomposition of space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.

\begin{lemma}
For $k\geq1$,
it holds
\begin{equation}\label{eq:Vdivlocaldecomp}
\boldsymbol{V}_{k-1}^{\rm div}(K)=\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus (\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{\max\{k-2,0\}}(K).
\end{equation}
Then the complex
\begin{equation*}
\boldsymbol{V}_{k}^{d-2}(K)\xrightarrow{\div\skw}\boldsymbol{V}_{k-1}^{\rm div}(K)\xrightarrow{\div} \mathbb P_{\max\{k-2,0\}}(K)\to0    
\end{equation*}
is exact.
\end{lemma}
\begin{proof}
We only prove the case $k\geq2$, as the proof for case $k=1$ is similar.
Since $\div:(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\to\mathbb P_{k-2}(K)$ is bijective \cite[Lemma 3.1]{ChenHuang2021divdiv}, we have $\div\skw \boldsymbol{V}_{k}^{d-2}(K)\cap(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)=\{\boldsymbol{0}\}$. Clearly $\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\subseteq \boldsymbol{V}_{k-1}^{\rm div}(K)$.

On the other side, for $\boldsymbol{\phi}\in \boldsymbol{V}_{k-1}^{\rm div}(K)$, by $\div\boldsymbol{\phi}\in \mathbb P_{k-2}(K)$, there exists a $q\in\mathbb P_{k-2}(K)$ such that $\div((\boldsymbol{x}-\boldsymbol{x}_K)q)=\div\boldsymbol{\phi}$, i.e. $\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$. Thanks to finite element complex \eqref{eq:localBDMfemderhamcomplex}, $\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\div\skw \boldsymbol{V}_{k}^{d-2}(K)$. Thus \eqref{eq:Vdivlocaldecomp} follows.
\end{proof}

Based on the space decomposition \eqref{eq:Vdivlocaldecomp} and the degrees of freedom of BDM element, we propose the following DoFs for space $\boldsymbol{V}_{k-1}^{\rm div}(K)$
\begin{align}
    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F^{\partial}(\mathcal T_K), \label{Vdivdof1}\\
    (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vdivdof2} \\
    (\boldsymbol{\phi}, \boldsymbol{q})_K & \quad\forall~\boldsymbol{q}\in \div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)=\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vdivdof3}
\end{align}
% where $\mathring{\boldsymbol{V}}_{k-1}^{\rm div}(K):=\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\boldsymbol{H}_0(\div, K)$.
% where $\mathcal E^{\partial}(\mathcal T_K):=\{e\in\mathcal E(\mathcal T_K): e\subset\partial K\}$.
% DoF \eqref{Vdivdof3} will disappear when $\mathcal T_K=\{K\}$ is a simplex.
\begin{lemma}
The set of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} is uni-solvent for space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.
\end{lemma}
\begin{proof}
By \eqref{eq:20220324-4} and \eqref{eq:Vdivlocaldecomp},
the number of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} is
\begin{align*}
&\quad {k+d-2\choose d-1}\#\mathcal F^{\partial}(\mathcal T_K)+\dim\mathbb P_{\max\{k-2,0\}}(K)-1+\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K) \\
&=\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)+\dim\mathbb P_{\max\{k-2,0\}}(K)=\dim\boldsymbol{V}_{k-1}^{\rm div}(K).
\end{align*}
% By \eqref{eq:Vdivlocaldecomp},
% the number of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} equals to $\dim\boldsymbol{V}_{k-1}^{\rm div}(K)$.

Assume $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$ and all the DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} vanish. By the vanishing DoF~\eqref{Vdivdof1}, $\boldsymbol{\phi}\in \boldsymbol{H}_0(\div, K)$ and $\div\boldsymbol{\phi}\in L_0^2(K)$. Then it follows from the vanishing DoF~\eqref{Vdivdof2} that $\div\boldsymbol{\phi}=0$. 
Thanks to the exactness of complexes \eqref{eq:localBDMfemderhamcomplex0}-\eqref{eq:localRTfemderhamcomplex0}, $\boldsymbol{\phi}\in\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)$. Therefore $\boldsymbol{\phi}=\boldsymbol{0}$ holds from the vanishing DoF~\eqref{Vdivdof3}.
\end{proof}

@@

Next we consider the norm equivalence of space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.

>>>>

% REQUIRED
\begin{abstract}
Virtual element methods (VEMs) without extrinsic stabilization in arbitrary degree of polynomial are developed for second order elliptic problems, \XH{including a nonconforming VEM and a conforming VEM in arbitrary dimension under the mesh assumption that all the faces of each polytope are simplices}. The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm. Optimal error estimates are derived for these VEMs. Numerical experiments are provided to test the VEMs without extrinsic stabilization.
\end{abstract}

@@

% The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
% the analysis is rather elaborate. 
% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, \XH{including a nonconforming VEM and a conforming VEM in arbitrary dimension under the mesh assumption that all the faces of each polytope are simplices}, in a unified way.
The key to construct VEMs without extrinsic stabilization is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
inner product $(\cdot, \cdot)_K$. The norm equivalence
\eqref{intro:gradVknormequiv} implies that the space $\mathbb{V}(K)$ should be
sufficiently large compared with the virtual element space $V_k(K)$.  In
standard virtual element methods, $Q_{k-1}^{K}\nabla v$
\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
space $\mathbb P_{k}(K)$.  While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then an additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.
% $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
% Instead, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.

We first construct $H(\div)$-conforming macro finite elements based on a
simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The
shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$-th
order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition
$\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element
space for $k=0$, with some constraints. To ensure the $L^2$ projection
$Q_{K,k}^{\div}\nabla v$ onto the space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
for virtual element function $v\in V_k(K)$, we require that
$\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
$\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$
is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
these considerations and the direct decomposition of the $H(\div)$-conforming
macro finite element space $\mathbb{V}_{k}^{\rm div}(K)$, we propose
the unisolvent DoFs for the space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
$L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
a conforming finite element for the differential $(d-2)$-form in
\cite{ArnoldFalkWinther2006,Arnold2018}.

@@

By the aid of the projector $Q_{K,k}^{\div}$, \XH{we advance a nonconforming VEM and a conforming VEM without extrinsic stabilization for second order elliptic problems in arbitrary dimension.}
Indeed, these VEMs can be equivalently recast as
primal mixed VEMs.
We prove the norm equivalence~\eqref{intro:gradVknormequiv} and the well-posedness of the VEMs without extrinsic stabilization, and derive the optimal error estimates.

@@

The rest of this paper is organized as follows. Notation and mesh conditions are presented in Section~\ref{sec:prelim}. 
In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed. A nonconforming VEM without extrinsic stabilization in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a conforming VEM without extrinsic stabilization in arbitrary dimension is devised in Section \ref{sec:stabfreecfmvem}.
Some numerical results are shown in Section \ref{sec:numericalexamps}.

@@

Given a $d$-dimensional polytope $K$, \XH{let $\Delta_j(K)$ be the set of all $j$-dimensional faces of $K$ for $j=0,1,\ldots, d-1$. Set $\mathcal{F}(K):=\Delta_{d-1}(K)$ and $\mathcal{E}(K):=\Delta_{d-2}(K)$.}
% let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ the unit outward normal vector to $\partial K$, which will be abbreviated as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.

@@

\subsection{Mesh conditions}\label{sec:meshcondition}
We impose the following conditions on the mesh $\mathcal T_h$ in this paper:
\begin{itemize}
 \item[(A1)] Each element $K\in \mathcal T_h$ and each face $F\in \mathcal F_h^r$ for $1\leq r\leq d-1$ is star-shaped with a uniformly bounded chunkiness parameter. \XH{All the $(d-1)$-dimensional faces of $K$ are simplices.}

 \item[(A2)] There exists a shape-regular simplicial mesh $\mathcal T_h^*$ such that each $K\in \mathcal T_h$ is a union of some simplexes in $\mathcal T_h^*$. For polytope $K\in \mathcal T_h$, let $\mathcal T_K$ be the simplicial partition of $K$ induced from $\mathcal T_h^*$. Assume simplicial partition $\mathcal T_K$ is quasi-uniform, \XH{and all the $(d-1)$-dimensional faces of $K$ are also faces of $\mathcal T_K$.}
\end{itemize}

@@

% For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. 
% Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. 
% Set 
% \[
% \mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
% \]

@@

Note that $\div\skw=\curl$ for $d=2,3$.
For $k\geq1$, by finite element complexes \eqref{eq:localBDMfemderhamcomplex}-\eqref{eq:localRTfemderhamcomplex0}, we have
\begin{equation}\label{eq:20220324-4}
\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)-\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\XH{\mathcal F(K)}-1.
\end{equation}
% \begin{align*}  
% \dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\mathcal F(\mathcal T_K)+ \left(d{k+d-2\choose d}-{k+d-1\choose d}\right)\#\mathcal T_K, \\
% \dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\mathcal F^i(\mathcal T_K)+ \left(d{k+d-2\choose d}-{k+d-1\choose d}\right)\#\mathcal T_K+1,
% \end{align*}

\subsection{$H(\div)$-conforming macro finite element}
For each polygon $K\in \mathcal T_h$, 
define the shape function space
\[
\XH{\mathbb{V}_{k-1}^{\rm div}(K)}:=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\},
\]
for $k\geq 2$, and 
\[
\XH{\mathbb{V}_{0}^{\rm div}(K)}:=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{\mathrm{RT}}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\}.
\]
Apparently $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\XH{\mathbb{V}_{k-1}^{\rm div}(K)}$, $\XH{\mathbb{V}_{0}^{\rm div}(K)}\cap\ker(\div)=\boldsymbol{V}_0^{\mathrm{RT}}(K)\cap\ker(\div)$, and $\XH{\mathbb{V}_{k-1}^{\rm div}(K)}\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$ for $k\geq2$.

In the following lemma we present a direct sum decomposition of space $\XH{\mathbb{V}_{k-1}^{\rm div}(K)}$.

\begin{lemma}
For $k\geq1$,
it holds
\begin{equation}\label{eq:Vdivlocaldecomp}
\XH{\mathbb{V}_{k-1}^{\rm div}(K)}=\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus (\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{\max\{k-2,0\}}(K).
\end{equation}
Then the complex
\begin{equation*}
\boldsymbol{V}_{k}^{d-2}(K)\xrightarrow{\div\skw}\mathbb{V}_{k-1}^{\rm div}(K)\xrightarrow{\div} \mathbb P_{\max\{k-2,0\}}(K)\to0    
\end{equation*}
is exact.
\end{lemma}
\begin{proof}
We only prove the case $k\geq2$, as the proof for case $k=1$ is similar.
Since $\div:(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\to\mathbb P_{k-2}(K)$ is bijective \cite[Lemma 3.1]{ChenHuang2021divdiv}, we have $\div\skw \boldsymbol{V}_{k}^{d-2}(K)\cap(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)=\{\boldsymbol{0}\}$. Clearly $\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\subseteq \XH{\mathbb{V}_{k-1}^{\rm div}(K)}$.

On the other side, for $\boldsymbol{\phi}\in \XH{\mathbb{V}_{k-1}^{\rm div}(K)}$, by $\div\boldsymbol{\phi}\in \mathbb P_{k-2}(K)$, there exists a $q\in\mathbb P_{k-2}(K)$ such that $\div((\boldsymbol{x}-\boldsymbol{x}_K)q)=\div\boldsymbol{\phi}$, i.e. $\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\XH{\mathbb{V}_{k-1}^{\rm div}(K)}\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$. Thanks to finite element complex \eqref{eq:localBDMfemderhamcomplex}, $\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\div\skw \boldsymbol{V}_{k}^{d-2}(K)$. Thus \eqref{eq:Vdivlocaldecomp} follows.
\end{proof}

Based on the space decomposition \eqref{eq:Vdivlocaldecomp} and the degrees of freedom of BDM element, we propose the following DoFs for space \XH{$\mathbb{V}_{k-1}^{\rm div}(K)$}
\begin{align}
    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\XH{\mathcal F(K)}, \label{Vdivdof1}\\
    (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vdivdof2} \\
    (\boldsymbol{\phi}, \boldsymbol{q})_K & \quad\forall~\boldsymbol{q}\in \div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)=\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vdivdof3}
\end{align}
% where $\mathring{\boldsymbol{V}}_{k-1}^{\rm div}(K):=\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\boldsymbol{H}_0(\div, K)$.
% where $\mathcal E^{\partial}(\mathcal T_K):=\{e\in\mathcal E(\mathcal T_K): e\subset\partial K\}$.
% DoF \eqref{Vdivdof3} will disappear when $\mathcal T_K=\{K\}$ is a simplex.
\begin{lemma}
The set of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} is uni-solvent for space \XH{$\mathbb{V}_{k-1}^{\rm div}(K)$}.
\end{lemma}
\begin{proof}
By \eqref{eq:20220324-4} and \eqref{eq:Vdivlocaldecomp},
the number of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} is
\begin{align*}
&\quad {k+d-2\choose d-1}\#\XH{\mathcal F(K)}+\dim\mathbb P_{\max\{k-2,0\}}(K)-1+\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K) \\
&=\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)+\dim\mathbb P_{\max\{k-2,0\}}(K)=\dim\XH{\mathbb{V}_{k-1}^{\rm div}(K)}.
\end{align*}
% By \eqref{eq:Vdivlocaldecomp},
% the number of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} equals to $\dim\boldsymbol{V}_{k-1}^{\rm div}(K)$.

Assume $\boldsymbol{\phi}\in\XH{\mathbb{V}_{k-1}^{\rm div}(K)}$ and all the DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} vanish. By the vanishing DoF~\eqref{Vdivdof1}, $\boldsymbol{\phi}\in \boldsymbol{H}_0(\div, K)$ and $\div\boldsymbol{\phi}\in L_0^2(K)$. Then it follows from the vanishing DoF~\eqref{Vdivdof2} that $\div\boldsymbol{\phi}=0$. 
Thanks to the exactness of complexes \eqref{eq:localBDMfemderhamcomplex0}-\eqref{eq:localRTfemderhamcomplex0}, $\boldsymbol{\phi}\in\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)$. Therefore $\boldsymbol{\phi}=\boldsymbol{0}$ holds from the vanishing DoF~\eqref{Vdivdof3}.
\end{proof}

@@

Next we consider the norm equivalence of space \XH{$\mathbb{V}_{k-1}^{\rm div}(K)$}.
